$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-28 paper/e6ssm-tuning-paper.tex
Removed a comma, made sure abbreviations are defined in the abstract

The discovery of a 125 GeV Higgs boson and rising lower bounds on the
masses of superpartners, have lead to concerns that supersymmetric
models are now fine tuned.  Large stop masses, required for a $125$
GeV Higgs, feed into the EWSB conditions through renormalisation group
equations forcing one to fine tune these parameters to obtain the
correct electroweak vacuum expectation value.  Nonetheless this fine
tuning depends crucially on our assumptions about the SUSY breaking
scale.  At the same time U(1) extensions provide the most compelling
solution to the $\mu$-problem, which is also a naturalness issue.
These very well motivated supersymmetric models predict a new
$Z^\prime$ boson which could be discovered at the LHC and the
naturalness of the model requires that the $Z^\prime$ boson mass
should not be too far above the TeV scale.  Moreover this fine tuning
appears at the tree level, making it less dependent on assumptions
about the SUSY breaking mechanism.  Here we study this fine tuning for
several $U(1)$ supersymmetric extensions of the standard model and
compare it to the situation in the MSSM where the most direct tree
level fine tuning can be probed through chargino mass limits.  We show
that future LHC $Z^\prime$ searches are extremely important for
challenging the most natural scenarios in these models.

>>>>

The discovery of a 125 GeV Higgs boson and rising lower bounds on the
masses of superpartners have lead to concerns that supersymmetric
models are now fine tuned.  Large stop masses, required for a $125$
GeV Higgs, feed into the electroweak symmetry breaking conditions 
through renormalisation group equations forcing one to fine tune these 
parameters to obtain the correct electroweak vacuum expectation value.  
Nonetheless this fine tuning depends crucially on our assumptions about 
the supersymmetry (SUSY) breaking scale.  At the same time U(1) extensions
provide the most compelling solution to the $\mu$-problem, which is also 
a naturalness issue. These very well motivated supersymmetric models 
predict a new $Z^\prime$ boson which could be discovered at the LHC and the
naturalness of the model requires that the $Z^\prime$ boson mass
should not be too far above the TeV scale.  Moreover this fine tuning
appears at the tree level, making it less dependent on assumptions
about the SUSY breaking mechanism.  Here we study this fine tuning for
several $U(1)$ supersymmetric extensions of the Standard Model and
compare it to the situation in the MSSM where the most direct tree
level fine tuning can be probed through chargino mass limits.  We show
that future LHC $Z^\prime$ searches are extremely important for
challenging the most natural scenarios in these models.
